---
title: "Presentation Project"
author: "Daniela Chávez"
date: "15/4/2021"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Presentation

The activity's purpose is to to show some of the characteristics of a Shiny application, a page was made that requests information from the student (thought of a child from 8 to 9 years old), using radiobuttons, graphics, tabs, etc. to do basic arithmetic with two numbers, tabulating and graphing their results. 

## Steps

1. The user type a name, two numbers and chose an arithmetic operation
2. The screen is divided into two parts, one where the data is entered (sidebar) and the other (mainbar) where the results are shown in two tabs

## My app

```{r primera}
library(shiny)
operaciones<-c("Add","Substract","Multiply","Divide")
tags$h4("This is an exercise designed for childrens ages 8-9")
inputPanel(
  textInput("box1","What's your name?:", value="My name is" ),
            numericInput("numeric1","Enter first number", value=0, min = 0, max = 100,step=1),
            numericInput("numeric2","Enter second number",value = 0, min=0, max = 100,step= 1),
            radioButtons("opc","Operation",operaciones)
)


```


## Outcomes

```{r Resultados}
renderText(input$box1) 
    model<-reactive({
        X<-input$numeric1
        Y<-input$numeric2
        if(input$opc=="Add")
            multi<-X+Y
        else if(input$opc=="Substract")
            multi<-X-Y
        else if(input$opc=="Divide")
            multi<-X/Y
        else multi<-X*Y
    })
    
    renderText({paste("You choose:",input$opc)})
    renderText({paste("Answer: ",model())})
    
    model2<-reactive({
    s<-input$numeric1+input$numeric2
    r<-input$numeric1-input$numeric2
    m<-input$numeric1*input$numeric2
    d<-input$numeric1/input$numeric2
    d<-data.frame("Order"=c("1","2","3","4"),"Operation"=c("Add","Substract","Multiply","Divide"), "Outcome"=c(s,r,m,d))
    })
    tags$h4(br(), "The next tab shows all outputs")
    renderTable(model2())
```


